\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item \fontsize{8.5pt}{9.8pt}\selectfont{
      {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \small\textbf{#1} & \small #2 \\
  \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \small#1 & \textit{\small #2} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Vikas Pedapudi} \\ \vspace{1pt}
\small +91 8179392569 $|$ \href{mailto:vikaspedapudi@gmail.com}{\underline{vikaspedapudi@gmail.com}} $|$
\href{https://linkedin.com/in/vikaspedapudi}{\underline{linkedin.com/in/vikaspedapudi}} $|$
\href{https://github.com/vikaspedapudi}{\underline{github.com/vikaspedapudi}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Institute of Technology, Warangal}{\small CGPA: 7.59/10}
{Bachelor of Technology in Electronics and Communication Engineering}{Jul. 2016 -- Aug. 2020}
\resumeSubheading
{Narayana Junior College, Marikavalasa}{Score\small: 980/1000}
{Intermediate in MPC (Maths, Physics, Chemistry) - BIEAP}{Jun. 2014 -- Apr. 2016}
\resumeSubheading
{St. Mary's High School, Yellamanchili}{\small GPA: 9.8/10}
{Class X - Secondary School Certificate (SSC) - BSEAP}{Jun. 2013 -- Apr. 2014}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Netcracker Technology}{Hyderabad, IN}
{Software Engineer}{July 2022 -- Present}
\resumeItemListStart
\resumeItem {Developing next-generation cloud-based billing application (Cloud NRM) as part of core R\&D team using C++, Kubernetes, Docker, AWS, WSL, and Postman.}
\resumeItem {Implemented 65+ features on billing \& finance sub-systems and supported bug fixes for clients including AIS, Altice Portugal, Andorra Telecom, BT, Fastweb, NTT, Nuuday, Telenet, and VMO2.}
\resumeItem {Developed a ProtoBuf-XML (PB2XML) marshaller as an independent utility library in NRM.}
\resumeItem {Improved Vertex tax library integration for billing, resulting in a 3.5x faster execution time and a 250\% performance improvement by processing 5.1 million events in 41 minutes.}
\resumeItem {Optimized database by 84.93\% with proper schema handling for test suites in billing and rating applications.}
\resumeItem {Applied DevOps practices including CI/CD pipelines, containerization, and infrastructure-as-code.}
\resumeItemListEnd
\resumeSubSubheading
{Junior Software Engineer}{October 2020 -- June 2022}
\resumeItemListStart
\resumeItem {Upgraded classic NRM code base to RHEL 8.2, GCC 8.3.x, and C++17.}
\resumeItem {Performed Just In Time Rollups (JITR) of new features, bug fixes, and fixed regression test suites.}
\resumeItem {Integrated NRM with Tax SaaS provider Vertex O Series for British Telecom DigiCo.}
\resumeItem {Automated functional and unit testing in builds using shell scripts and GTest framework.}
\resumeItem {Implemented SEPA support for Andorra Telecom in Cloud NRM.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://drive.google.com/drive/folders/1RTOW_ngAQwRtwY2WZIVu-BZbX9ZryLW5?usp=drive_link}{Detection and Classification of Eye Diseases}} $|$ \emph{Python, Keras, TensorFlow}}{Jul 2019 -- Apr 2020}
\resumeItemListStart
\resumeItem{Led a team of three to develop a multi-class classifier using Convolutional Neural Networks to classify the eye diseases from the Retinal Fundus Images in 4 classes namely Cataracts, Diabetic Retinopathy, Glaucoma, and Normal. Achieved a classification accuracy of 84\%}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Implementation of AES on FPGA} $|$ \emph{VHDL}}{Mar -- Apr 2018}
\resumeItemListStart
\resumeItem{Developed VHDL code for the 128-bit AES encryption algorithm and implemented it on Nexys 4 DDR Artix-7 FPGA Board}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{8086 Based Microprocessor Project} $|$ \emph{Assembly Language}}{Feb 2019}
\resumeItemListStart
\resumeItem{Interfaced both Hex-keypad and 7-segment display together with the 8086 microprocessor using 8255 PPI, so that the key pressed in the hex-keypad gets serially displayed in the SSD}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Obstacle Avoiding Vehicle using Arduino} $|$ \emph{Arduino Programming (C/C++)}}{Mar -- Apr 2019}
\resumeItemListStart
\resumeItem{Designed a vehicle with an ultrasonic sensor mounted on a servo motor to detect obstacles and find alternative paths. Interfaced components with Arduino UNO}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Core Competencies}{: C/C++, Oracle SQL, PostgreSQL, Shell scripting} \\
\textbf{Platforms}{: Windows, Linux/Unix} \\
\textbf{Technologies \& Tools}{: CUDA, Python, Kubernetes, Git, WSL, Docker, CLion, Bazel, Postman, Jenkins, CI/CD, Jira} \\
}}
\end{itemize}

%-----------ACADEMIC ACHIEVEMENTS-----------
\section{Academic Achievements}
\begin{itemize}[left=5pt, itemsep=0pt, topsep=0pt, label=\raisebox{0.25ex}{\footnotesize$\bullet$}]
\resumeItem {Awarded the \textbf{‘Above and Beyond’} at Netcracker Technology for Cloud NRM contributions to Nuuday, Altice, Fastweb, and AIS.} \hfill \textit{2024}
\resumeItem {Led a team of five to develop the 'BillData as ProtoBuf' solution, earning a consolation prize at the \textbf{Netracker Hackathon}.} \hfill \textit{2023}
\resumeItem {Awarded the \textbf{‘You've Made a Difference’} at Netcracker Technology for significant contributions to Cloud NRM development.} \hfill \textit{2023}
\resumeItem {Received the \textbf{‘Team Award - Champions’} at Netcracker for my contributions to the successful NRM RHEL 8.2 upgrade project.} \hfill \textit{2021}
\resumeItem {Presented a project on "Briquetting of Agro Waste" at the \textbf{A.P. State Level 20th National Children's Science Congress}.} \hfill \textit{2012}
\resumeItem {Won 3rd Prize in the \textbf{District Educational Science Exhibition} for the exhibit under the sub-theme "Mathematical Modelling" under the theme of "Science and Society"} \hfill \textit{2012-13}
\resumeItem {Secured 1st Prize in Quiz Competition at the \textbf{District Inspire Exhibition}.} \hfill \textit{2011-12}
\resumeItem {Honored as \textbf{'Best Student'} at St. Mary’s Silver Jubilee, awarded a gold medal and memento.} \hfill \textit{2013-14}
\end{itemize}

%-----------EXTRACURRICULAR ACTIVITIES-----------
\section{Extracurricular Activities}
\begin{itemize}[left=5pt, itemsep=0pt, topsep=0pt, label=\raisebox{0.25ex}{\footnotesize$\bullet$}]
\resumeItem {Joint Treasurer, NIT Warangal Alumni Association, Hyderabad Chapter (NITWAAH) \textbf{--} Managing finances and alumni events.} \hfill \textit{2022-Ong}
\resumeItem {Sub-Coordinator, Event Conduction and Coordination (ECC), Technozion, NIT Warangal \textbf{--} Coordinated Technozion events.} \hfill \textit{2017-19}
\resumeItem {Software Developer, Web \& Software Development Cell (WSDC), NIT Warangal \textbf{--} Maintained student portal for 7,000+ users.} \hfill \textit{2016-19}
\resumeItem {House Leader, St. Mary’s High School \textbf{--} Led inter-house activities, promoting teamwork and school spirit.} \hfill \textit{2012-14}
\end{itemize}

\end{document}